---
title: "Terror"
author: "Aaron Skipper"
date: "10/7/2018"
output: html_document
---

```{r basicfcn, include=F}
# can add quietly=T option to the require() function
loadPkg = function(x) { if (!require(x,character.only=T, quietly =T)) { install.packages(x,dep=T,repos="http://cran.us.r-project.org"); if(!require(x,character.only=T)) stop("Package not found") } }
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r base_lib, include=FALSE}
loadPkg("dplyr")
loadPkg("tidyr")
loadPkg("tidyverse")
loadPkg("ggplot2")
loadPkg("Rmisc")  # CI function for confidence interval, single vector
loadPkg("corrplot")
loadPkg("car")
#library(tidyverse)
#library(car)
```


```{r setup0, include=T}
ter <- data.frame(read.csv("globalterrorismdb_0718dist.csv"))
#colnames(ter)
```

### DISCOVERY.  Many columns, may want to see if we can eliminate the ones that we dont have interest in, or we can keep.

```{r ESDA, include=TRUE}
#summary(ter)
#str(ter)
```







### Number of Kills by Weapon Type- Slide 32

```{r setup1, include=T}
library(ggplot2)
ggplot(data=ter) + geom_bar(stat="identity", mapping=aes(x=targtype1_txt,y=nkill, color = weaptype1_txt))
```

```{r setup2, include=T}
ter_us <- filter(ter, country_txt == "United States")
```

###big spike noted for 9/11/01 colvolutes the data

```{r setup22, include=T}
t_us <- aggregate(nkill ~ iyear, ter_us, sum)
ggplot(data=t_us) + geom_area(mapping = aes(x=iyear, y=nkill))
# removing that year - 9/11 2001
t_us1 <- t_us[-c(31), ]
ggplot(data=t_us1) + geom_area(mapping = aes(x=iyear, y=nkill))
```


###notice that 1995 and 2017 have large spikes- may want to 
### investigate further for those years



### number of kills by year


```{r setup4, include=TRUE}
ggplot(data=ter) + geom_bar(stat="identity",mapping = aes(x=iyear, y=nkill))
```







### This is slide 31- Except for this, it's showing the line representing the # of attacks, and the bars showing the number of kills.


### number of kills with the number of attacks, by year. 

```{r setup5, include=TRUE}
ter_attack<-aggregate(attacktype1 ~ iyear, ter, sum)
ggplot(data=ter) + geom_bar(stat="identity",mapping = aes(x=iyear, y=nkill)) + geom_line(data=ter_attack, mapping=aes(x=iyear, y=attacktype1, colour="blue"))
```
### This is the reverse from the slide. Shows the number of attacks for the line, overlaying the bar graph of total kills.
